A Bioconductor Workflow for Processing and Analysing Spatial Proteomics Data

### 2016-12-01 bioc-workflow.Rnw

\subsection*{Features of interest}
In addition to adding annotation using the \texttt{addMarkers}
function one can store specific sets of proteins by using the
\textit{Features of interest} infrastructure from the
\Biocpkg{MSnbase} package. If users have a specific subset of proteins
they wish to highlight in their data they would first create a
\texttt{FeaturesOfInterest} object. For example, if we wanted to
highlight a proteins with the accession numbers Q8CG48, Q8CG47,
Q8K2Z4, and Q8C156, which are some of the proteins known to form part
of the 13S condensin complex, we would create a first create a
\texttt{FeaturesOfInterest} object then use the function
\texttt{highlightOnPlot} to highlight their location on a PCA plot.

@@

plot2D(hl)
addLegend(hl, cex = .6)
highlightOnPlot(hl, foi13s)
@  
  \caption{Highlighting protein features of interest}
  \label{fig:foi}
\end{figure}

@@

It is also worthly of note that it is possible to search for a
specific protein of interest by \texttt{featureNames} or using any
identifying information found in the \texttt{fData} columns by using
the search box on the \texttt{pRolocVis} application part of the
\Biocpkg{pRolocGUI} package (see section on interactive
visualisation). This can be handy for quickly searching and
highlighting proteins on the fly, the disavanatge here is that
proteins can only be searched for a one-by-one basis.

>>>>

\subsection*{Features of interest}
In addition to adding annotation using the \texttt{addMarkers}
function, one can store specific sets of proteins by using the
\textit{Features of interest} infrastructure from the
\Biocpkg{MSnbase} package. If users have specific subsets of proteins
they wish to highlight in their data (possibly across multiple
experiments) they would first create a \texttt{FeaturesOfInterest}
object. For example, if we wanted to highlight a proteins with the
accession numbers Q8CG48, Q8CG47, Q8K2Z4, and Q8C156, which are some
of the proteins known to form part of the 13S condensin complex, we
would create a first create a \texttt{FeaturesOfInterest} object, and
subsequently highlight their location on a PCA plot with the
\texttt{highlightOnPlot} function.

@@

plot2D(hl)
addLegend(hl, cex = .6)
highlightOnPlot(hl, foi13s)
@  
  \caption{Highlighting protein features of interest.}
  \label{fig:foi}
\end{figure}

@@

It is also worthy of note that it is possible to search for a
specific protein of interest by \texttt{featureNames} or using any
identifying information found in the \texttt{fData} columns by using
the search box on the \texttt{pRolocVis} application part of the
\Biocpkg{pRolocGUI} package (see section on interactive
visualisation). This can be handy for quickly searching and
highlighting proteins on the fly, the disavanatge here is that
proteins can only be searched for a one-by-one basis.
